---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggthemes)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(GGally)
library(alr3)
library(caret)
library(class)
library(MASS)
library("ggpubr")
library(boot)
library(broom)
```
\section{Q2.}


```{r}
library(ISLR)
data("College")
College$Accept.Apps<-College$Accept/College$Apps
College<-College[,c(-2,-3)]
#Split the dataset
set.seed(234)
inTrain <- createDataPartition(College$Accept.Apps, p = 0.7, list = FALSE)
training <- College[inTrain,]
testing <- College[-inTrain,]
```
__(a)__
```{r}
X <- model.matrix(Accept.Apps ~ ., data = College)[, -1]
# Run PCA
collegePCA <- prcomp(x = X, center = T, scale = T)
```
We Choose to standardize our data, Since the scales of different variables vary a lot. 
```{r}
collegePCA
#Scree Plot
plot(collegePCA)
```
We need 14 eigenvalues for us to explain 95% of the variances in the data.
```{r}
#loadings fo the first and second PCs
collegePCA$rotation[,1]
collegePCA$rotation[,2]
```
The first component is proportional to each variable, and the second component measures the difference between the first pair of variables and the second pair of variables.

__(b)__
```{r}
library(pls)
collegePCR <- pcr(Accept.Apps ~ ., data = training, scale = TRUE, validation = "CV")
summary(collegePCR)

validationplot(collegePCR, val.type = "MSEP", legendpos = "topright")
```
Hence the value m is chosen with 14
```{r}
collegePCR.pred <- predict(collegePCR, College[-inTrain, names(College) != 'Salary'], ncomp = 14)
PCRTestMSE <- mean((collegePCR.pred - College[-inTrain, "Accept.Apps"])^2)
PCRTestMSE #test error obtained
```
__(C)__
```{r}
PCRTestMSE
#                 TestMSE     TrainMSE
#Best reduced OLS	0.01441521	0.01315906		
#Ridge Regression	0.01432566	0.01334943		
#Lasso	          0.01554418	0.01405796	

```
The PC regression performs the lowest testMSE for this dataset. Although it requires
a lot of calculation, the differences of the testMSEs are significant. So PCR should be chosen as
the approach to analyze this dataset.
